Evaluating Informative Hypotheses with Equality and Inequality Constraints:\\ A Tutorial Using the Bayes Factor via the Encompassing Prior Approach

### 2021-11-28 Documents/Paper/paper.Rnw
add affiliation paper

\author{Claudio Zandonella Callegher$^1$, Tatiana Marci$^1$, Pietro De Carli$^2$, Gianmarco Altoè$^1$}
\affiliation{$^1$UNIPD\\$^2$UNIMI}

@@

All analyses were conducted using R statistical software \parencite[v\Sexpr{paste(version$major,version$minor, sep = ".")};][]{rcoreteamLanguageEnvironmentStatistical2021}. All materials, data, and analysis code are available at \url{https://github.com/ClaudioZandonella/Attachment}. Supplemental Material with further details is also available online at \url{https://claudiozandonella.github.io/Attachment/}.

>>>>

\author{Claudio Zandonella Callegher$^1$, Tatiana Marci$^1$, Pietro De Carli$^2$, Gianmarco Altoè$^1$}
\affiliation{$^1$Department of Developmental Psychology and Socialization, University of Padova\\
$^2$UNIMI TODO }

@@

All analyses were conducted using R statistical software \parencite[v\Sexpr{paste(version$major,version$minor, sep = ".")};][]{rcoreteamLanguageEnvironmentStatistical2021}. All materials, data, and analysis code are available at \url{https://github.com/ClaudioZandonella/Attachment} [TDO add doi]. Supplemental Material with further details is also available online at \url{https://claudiozandonella.github.io/Attachment/}.
